%%%%% this line is 80 chars wide, please don't make longer lines %%%%%%%%%%%%%%%
The neuronal representation of sound is the result of the encoding of acoustic 
signals done through the peripheral auditory system. 
The spike trains resulting from this encoding are influenced, 
among other factors, by the refractory period of the 
auditory nerve fibers. 
We learn, for example, in \cite{AvissarPapier} that for the encoding of pure tones, 
the time-spike precision depends in part on the ratio of  
the refractory period to the stimulus period. 
We also know from the research of Berry and Meister described 
in \cite{BerryMeister} that the refractoriness of neurons may make their signals 
more reliable for temporal precision. 
Then, in \cite{Deger}, processes with refractoriness were studied 
and predictions 
were made for Fourier coefficients of response when the stimulus is a pure tone.%%

This project has for purpose to go further in the study the effects of 
the refractoriness on the spike-trains resulting from encoding in the peripheral 
auditory system.  
First, it will study this effect on an ad-hoc computation made on spike trains,  
the rate-modulation depth, for four kinds of stimuli.
Then, it will see if their Fourier coefficients match the predictions
of \cite{Deger}, for a modulated pure tone stimulus. 
Since we have phase-locking for a modulated pure tone stimulus 
as we have in the non-modulated one, we expect the same kind of effect of refractory 
period on the response.



%we have better entrainment of spike trains and often also better precision 
%in time encoding. 
%%%

%This project studied the effects of this neural property 
%on the resulting encoded spike trains. 

For this aim, a model of the peripheral auditory system was used
\cite{Model1, Model2, Model3}, in which the refractory period can be modified. 
Virtual experiments were run on the two versions of the model and the resulting 
spike trains were compared to see the influence of the refractory period. 
Before going any deeper on the model, we should remind us some things 
about the auditory system.

%Acoustic signals are encoded as spike trains by auditory nerve fibers. The time-dependent firing rate and other aspects of spike train statistics depend, among other things, on the refractory period of the nerve fibers. This project aims to understand the influence of the refractory period on the neuronal representation of sounds.

%A phenomenological model of the peripheral auditory system [1,2] will be used to perform virtual experiments. The model allows to modify the refractory period of the nerve fibers. The responses of the model to a selection of auditory stimuli will be recorded and characterized as a function of the neuronal refractory period. If time permits, specific theoretical predictions like frequency doubling [3] will be tested.
